---
title: "Cognitive Load in Interpreting and Translating"
subtitle: "DoKo Presentation"
author: "Matthias Kobi"
date: "`r format(Sys.time(), '%d %b %Y')`"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: 16:9
      countdown: 60000

---
```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

if (!"xaringan" %in% installed.packages()[, "Package"]) {
  install.packages("xaringan")
}

library(xaringan)
library(tikzDevice)
library(tidyverse)
library(tinytex)
library(png)
library(grid)
library(xtable)

#RFolder <- file.path("R") 

options(htmltools.dir.version = FALSE)
# see: https://github.com/yihui/xaringan
# install.packages("xaringan")
# see: 
# https://github.com/yihui/xaringan/wiki
# https://github.com/gnab/remark/wiki/Markdown
options(width=110)
options(digits = 4)
```



# Language Survey

- Age of Commencement

- Exposure

- Experience (cumulative training hours)

---
# Language Survey
```{r error=FALSE, warning=FALSE, message=FALSE, comment = ""}
load(file.path("data/hgf.Rdata"))
load(file.path("data/hgf_doubles.Rdata"))

hgf <- hgf %>% 
  filter(group != "IntPro", group != "IntMA", group != "IntBA") %>% 
  select(VPN_Code, group, cum_trainingh_DuU, Prozent_cumth_Life.x,hpd_DuU, hpd_ALLE, Prozent_ALLE_pd)

colnames(hgf) <- c("id", "group", "cumTH_U", "percCumTH_U", "HpD_U", "HpD_L", "percHpD_L")

glimpse(hgf)
```

---
# Language Survey

```{r error=FALSE, warning=FALSE, message=FALSE, comment = "", results = "asis"} 

doubles_df <- doubles_df %>% 
  select(VPN_Code, cum_trainingh_DuU, Prozent_cumth_Life.x,hpd_DuU)

colnames(doubles_df) <- c("id", "cumTH_U", "percCumTH_U", "HpD_U")

print(xtable(doubles_df,caption = "Doubled Datasets"), type = "html", html.table.attributes = "border=0")

```

---
# Extraordinary long days
```{r error=FALSE, warning=FALSE, message=FALSE, comment = "", results = "asis", echo=FALSE} 

hgf_res <- hgf %>% 
  filter(percCumTH_U >= 15 | percHpD_L >= 100)

DT::datatable(
  hgf_res,
  fillContainer = FALSE, options = list(pageLength = 8), editable = TRUE
)

#print(xtable(hgf_res,caption = "Extraordinary long days"), type = "html", html.table.attributes = "border=0")

```

---
# Language Survey
```{r error=FALSE, warning=FALSE, message=FALSE, comment = "", results = "asis"} 

hgf_res <- hgf %>% 
  group_by(group) %>% 
  summarise(meanCumTH_DuD = mean(cumTH_U), meanHpD_L = mean(HpD_L))

print(xtable(hgf_res,caption = "TraMa live longer!"), type = "html", html.table.attributes = "border=0")

```

---
# Language Survey
```{r error=FALSE, warning=FALSE, message=FALSE, comment = "", results = "asis"} 

hgf_res <- hgf %>% 
  filter(group == "TraMA")

print(xtable(hgf_res,caption = "Study Translating!"), type = "html", html.table.attributes = "border=0")

```

---
# WIE

Short form with 4 subtests:

- Gemeinsamkeiten finden

- Zahlen nachsprechen (vorwärts und rückwärts)

- Mosaik-Test

- Zahlensymboltest

--



T-Values

**Highly correlating with full WIE**

---
# WIE

```{r error=FALSE, warning=FALSE, message=FALSE, comment = "", results = "asis"} 
load(file.path("data/vpdata.Rdata"))

wie <- vpdata %>% 
  filter(!is.na(HAWIE_T_Value), id != "C24") %>% 
  group_by(group) %>%
  summarise(meanWIE = mean(HAWIE_T_Value), sdWIE = sd(HAWIE_T_Value))

print(xtable(wie,caption = "WIE"), type = "html", html.table.attributes = "border=0")
```

---
# Trail Making Test

- 2 subtests

- Processing speed

--

- Mean processing time and errors 

---
# Trail Making Test

```{r error=FALSE, warning=FALSE, message=FALSE, comment = "", results = "asis"} 

tmt <- vpdata %>% 
  filter(!is.na(t_TMT_A_in_s)) %>% 
  group_by(group) %>%
  summarise(meanTMT_A = mean(t_TMT_A_in_s), sdTMT_A = sd(t_TMT_A_in_s), meanF_A = mean(F_TMT_A), meanTMT_B = mean(t_TMT_B_in_s), sdTMT_B = sd(t_TMT_B_in_s),meanF_B = mean(F_TMT_B))

print(xtable(tmt,caption = "WIE"), type = "html", html.table.attributes = "border=0")
```

---
# N-Back

- 2 subtests (visual / auditory)

- 3-back with letters

- Working memory

--

- dPrimes, RT, Criterion

---
# N-Back

```{r warning= FALSE, message=FALSE, echo=FALSE}

source(file.path("R/Preprocessing/nback.R"))
#source(file.path("R/nback_analysing.R"))
```
